### 2020-11-03 codes/ali_test_sir.Rmd
some questions in smoothing

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=0.8,gamma=1/3, omega=0.25, rho=0.01, 
             W_s=1, W_i=1, W_r=1, #weights
             P_s=0, P_i=1, P_r=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_t=0.01, #isolation parameter 
            s=2, #eta_w/eta_t
            tau=1
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
d <- seq(0,200,by=0.1)
# Conditional stop for desolver
rootfun <- function (time, state,params) { 
  unpack(as.list(c(state,params)))
  return(I_u - 1) }
```

@@

```{r run2, message=FALSE}
d_long <- seq(0,400,by=0.1)
## capturing badly behaved integrator warning messages
cc <- capture.output(
    out_long <- as.data.frame(
        ode(
    func=sir.model,
    y=state_init,
    times= d_long, 
    parms=update(params,beta=2)
    # rootfun = rootfun,
    # method="lsodar"
  )
  ))
out_long2 <- out_long %>%
    pivot_longer(c(S_u,S_n,I_u,I_n,I_p,I_t, R_u,R_n,R_p,R_t),
                 names_to = "compartment", values_to = "value")

@@

The Eigenvalues of $G_{11}$, are 0 and $R_0$.
```{r R0}

F_i <- function(params){
   # Returns F_i at DFE 
  unpack(as.list(params))
  Su_dfe<- Su_dfe(params)
  Sn_dfe<- N0-Su_dfe
  sigma <- tau*rho*N0/(tau*(W_s*Su_dfe)+rho*N0) #at DFE 
  return(sigma*W_i)
}

@@

```{r contour_R0_2, message=FALSE,warning=FALSE }
 # specify the ranges
 beta  <- 0.5
 # eta_w <- seq(0,1, length.out=5) 
 eta_t <- seq(0.0001,0.5, length.out=n_out) #0.001 
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.001,1 , length.out=n_in) #note omega must be > 0, was 0.1
 s <- seq(1,2,length.out=n_out)

@@

df22<- data.frame(df11,R0=apply(df11,1,function(params_in)R02(params=params_in)),
                      Fi= apply(df11,1,function(params_in)F_i(params=params_in)),
                       Su=apply(df11,1,function(params_in)Su_dfe(params = params_in)))
# min(df22$Su)
# which(df22[]<0)          
```

>>>>

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=0.8,gamma=1/3, omega=0.25, rho=0.01, 
             W_s=.01, W_i=1, W_r=1, #weights
             P_s=0, P_i=1, P_r=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_t=0.01, #isolation parameter 
            s=2, #eta_w/eta_t
            tau=1
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
d <- seq(0,200,by=0.1)
# Conditional stop for desolver
rootfun <- function (time, state,params) { 
  unpack(as.list(c(state,params)))
  return(I_u - 1) }
```

@@

```{r run2, message=FALSE}
d_long <- seq(0,300,by=0.1)
## capturing badly behaved integrator warning messages
cc <- capture.output(
    out_long <- as.data.frame(
        ode(
    func=sir.model,
    y=state_init,
    times= d_long, 
    parms=update(params,beta=2)
    # rootfun = rootfun,
    # method="lsodar"
  )
  ))
out_long2 <- out_long %>%
    pivot_longer(c(S_u,S_n,I_u,I_n,I_p,I_t, R_u,R_n,R_p,R_t),
                 names_to = "compartment", values_to = "value")

@@

The Eigenvalues of $G_{11}$, are 0 and $R_0$.
```{r R0}
F_i <- function(params){
   # Returns F_i at DFE 
  unpack(as.list(params))
  Su_dfe<- Su_dfe(params)
  Sn_dfe<- N0-Su_dfe
  sigma <- tau*rho*N0/(tau*(W_s*Su_dfe)+rho*N0) #at DFE 
  return(sigma*W_i)
}

@@

```{r contour_R0_2, message=FALSE,warning=FALSE }
 # specify the ranges
 # beta  <- 0.5
 # eta_w <- seq(0,1, length.out=5) 
 # eta_t <- seq(0.001,0.5, length.out=n_out) #0.001 
 # rho     <- seq(0,0.01, length.out=n_in)
 # omega <- seq(0.001,1 , length.out=n_in) #note omega must be > 0, was 0.1
 s <- seq(1,2,length.out=n_out)

@@

df22<- data.frame(df11,R0=apply(df11,1,function(params_in)R02(params=params_in)),
                      Fi= apply(df11,1,function(params_in)F_i(params=params_in)),
                       Su=apply(df11,1,function(params_in)Su_dfe(params = params_in)))
```

### 2020-11-03 smoothing.tex
some questions in smoothing

- The initial approache and the singularity issue;
$\sigma = \frac{\rho N_0}{W}$ was used initially. The issue was that the population in $S$ compartments appeared to blow up when the DFE is achieved. This is  once the only untested people are susceptibles, the FoI will become $\Lambda=0$, testing rate $F_s=\rho N_0/S_u$. Thus, eq(1) of the model will be $d S_u/dt = - \rho N_0 + \omega S_n$ which is no longer dependent on $S_u$ and a linear rate of leaving the $S_u$ compartment.

- The secondary approache;
It was suggested that

@@

>>>>

- The initial approache and the singularity issue;

$\sigma = \frac{\rho N_0}{W}$ was used initially. The issue was that the population in $S$ compartments appeared to blow up when the DFE is achieved. This is  once the only untested people are susceptibles, the FoI will become $\Lambda=0$, testing rate $F_s=\rho N_0/S_u$. Thus, eq(1) of the model will be $d S_u/dt = - \rho N_0 + \omega S_n$ which is no longer dependent on $S_u$ and a linear rate of leaving the $S_u$ compartment.

- The secondary approache;

@@

\section{Questions};

1- When $\sigma=\rho$?  
  $\frac{\tau N0}{\tau W+ \rho N_0} = 1$. Mathematically, this can be achieved when $W \approx N_0$ and   $\tau \gg \rho$.

2- What is the most interesting thing in the testing strategies?
We intuitively know testing/tracing/isolation (TTI) strategy is more effective than random testing in the sense that it lowers the $R_0$. Obvious things to ask are

(i)  How much TTI is lowering $R_0$? 
(ii) How fast TTI is lowering $R_0$?
